The contribution of drifting snow to cloud properties and the atmospheric radiative budget over Antarctica

### 2022-05-02 submission/review_1/production_submission/agujournaltemplate.tex
Add production files for the paper

\subsubsection*{Open Research}

%The monthly means used in this study, from 1980-2100 of all three MAR RCP 8.5 simulations are available via ftp://ftp.climato.be/fettweis/MARv3.9/Greenland/. In case daily outputs are required, these can be requested from Xavier Fettweis (xavier.fettweis@uliege.be) and Stefan Hofer (s.hofer@bristol.ac.uk).
%
\textbf{Data and code owned by the authors:} all the code used for the analysis in this study is available on https://github.com/stefan-hofer/Antarctica\_clouds, but will be made available via zenodo upon acceptance of the manuscript. All the 2000-2019 averages from our MAR simulations with and without drifting snow are available via \hfill \break  https://zenodo.org/record/5037197.

@@

The weather station data used for comparison with MAR is a compilation of various sources.\hfill \break 
\textbf{D17:} https://zenodo.org/record/4139737 \hfill \break 
\textbf{Dome\_C\_II:} freely downloaded from the BSRN website: https://bsrn.awi.de/ and via Pangea (https://doi.pangaea.de/10.1594/PANGAEA.935421) \cite{lupi2021}.\hfill \break 
\textbf{Halley:} From the British Antarctic Survey via: src@bas.ac.uk \hfill \break 
\textbf{Amundsen\_Scott:} Via BSRN and Pangea (https://doi.pangaea.de/10.1594/PANGAEA.150004) \cite{dutton2015}.\hfill \break 
\textbf{Neumayer, Sorasen et Panda-1:} can be downloaded via Pangea \\
(https://doi.pangaea.de/10.1594/PANGAEA.919128) \cite{schmithusen2020}. \hfill \break 
\textbf{From AWS4 to AWS19:} Via Pangea (https://doi.pangaea.de/10.1594/PANGAEA.910484) \cite{jakobs2020}. \hfill \break

@@

%Reference citation instructions and examples:
%
% Please use ONLY \cite and \citeA for reference citations.
% \cite for parenthetical references
% ...as shown in recent studies (Simpson et al., 2019)
% \citeA for in-text citations
% ...Simpson et al. (2019) have shown...
%
%
%...as shown by \citeA{jskilby}.
%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
%...has been shown \cite{jskilbye}.
%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown by \cite <e.g.,>[and others]{lewin76}.
%
% apacite uses < > for prenotes and [ ] for postnotes
% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
%

>>>>

\subsubsection*{Open Research}
%
\textbf{Data and code owned by the authors:} all the code used for the analysis in this study is archived on Zenodo under the DOI: 10.5281/zenodo.5596516. All the 2000-2019 averages from our MAR simulations with and without drifting snow are available via https://zenodo.org/record/5037197.

@@

The weather station data used for comparison with MAR is a compilation of various sources.\hfill \break 
\textbf{D17:} https://zenodo.org/record/4139737 \hfill \break 
\textbf{Dome\_C\_II:} freely downloaded from the BSRN website: https://bsrn.awi.de/ and via Pangea (https://doi.pangaea.de/10.1594/PANGAEA.935421) \cite{lupi2021}.\hfill \break 
\textbf{Halley:} General meteorological variables (temperature, wind, pressure) can be downloaded via https://doi.org/10.5285/4E963D9B-DA5D-43D5-A605-FC44EAD63D97 \cite{King2021}. Additional variables related to the surface energy budget (shortwave and longwave fluxes) can be requested via: src@bas.ac.uk \hfill \break 
\textbf{Amundsen\_Scott:} Via BSRN and Pangea (https://doi.pangaea.de/10.1594/PANGAEA.150004) \cite{dutton2015}.\hfill \break 
\textbf{Neumayer, Sorasen et Panda-1:} can be downloaded via Pangea \\
(https://doi.pangaea.de/10.1594/PANGAEA.919128) \cite{schmithusen2020}. \hfill \break 
\textbf{From AWS4 to AWS19:} Via Pangea (https://doi.pangaea.de/10.1594/PANGAEA.910473) \cite{jakobs2020}. \hfill \break

@@
